Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2020-11-16 GWLDCI.tex
minor changed in comments
referee M's comment on the bijecition

\todo{Need to address the summary comment to 3.1 in review M}

@@

>>>>

@@

\begin{rmk}
The previous lemma shows that $\tau$ does map into polygon dissections.  In fact $\tau$ is a bijection from weakly admissible Wilson loop diagrams to polygon dissections.  To see the inverse map, and hence obtain bijectivity, we need only reverse the construction above.  The only part which is nontrivial is that if diagonals of the dissection meet at a common vertex, we need to order the propagators associated to these diagonals along the edge associated to the vertex of the dissection, but using the noncrossing property of propagators this can be done uniquely.

The $\tau$ bijection will be useful, as is typical in bijective combinatorics, because some features are more visible on the dissection side.  In particular the exact subdiagrams are visible as triangulated pieces and equivalence comes down to retriangulation.  All of these notions are defined and explained below.

As a final note before we begin laying out the results we need on $\tau$, if a Wilson loop diagram $W$ is weakly admissible but not admissible, then the same equality that would give exactness in a subdiagram holds, and so for the same reasons as described below for exact subdiagrams $\tau(W)$ will have all triangle internal faces and this is the only way that $\tau(W)$ can have all triangle internal faces.  Therefore, $\tau$ also gives a bijection between admissible Wilson loop diagrams and polygon dissections with at least one non-triangle internal face.
\end{rmk}
